### 2019-03-22 Journal Version/binaryFDT.tex
journal

\section{Finding a feasible solution}\label{domTOIP}
Consider a formulation instance $I=(A,G,b)$. Define sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively. And assume $S(I),P(I)\in [0,1]^n\times \bbbr^p$. For simplicity in the notation we denote $P(I),S(I),$ and $g(I)$ with $P$, $S$, and $g$ for this section and the next section. Also, for both sections we assume $t=|\spp(x)|$. Without loss of generality we can assume $x_i = 0$ for $i=t+1,\ldots,n$.

In this section we prove Theorem \ref{domtoIP}. In fact, we prove a stronger result. 
\begin{lemma}\label{domlemma}
	Given $(x,y)\in \dom(P)$, there is an algorithm (the Dom2IP algorithm) that finds $(x^{(t)},y^{(t)})\in S$ in polynomial time, such that $x^{t}\leq x$, where $t=|\spp(x)|$\end{lemma}

We prove Lemma \ref{domlemma} by introducing an algorithm that ``fixes" the variables iteratively, starting from $x_1$ and ending at $x_t$. Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,t$. Now consider the following linear program. The variables of this linear program are the $z\in \bbbr^n$ variables and $w\in \bbbr^p$.
\begin{align}
	\DOMtoS(x^{(\ell)})\quad\quad& \min\quad \;z_{\ell+1}\\
	&\;\text{s.t.} \quad \;\;Az+ Gw\geq b \\
	&\;{\color{white}{\text{s.t.}} }\quad \;\; \; z_j = x^{(\ell)}_j \quad \; j =1,\ldots, \ell\\
	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z_j \leq x^{(\ell)}_j \quad \; j = \ell+1,\ldots,n\\
	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z\;\geq 0
\end{align}

If the optimal value to $\DOMtoS(x^{(\ell)})$ is 0, then let $x^{(\ell+1)}_{\ell+1} = 0$. Otherwise if the optimal value is strictly positive let $x^{(\ell+1)}_{\ell+1} = 1$. Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in \{1,\ldots,n\}\setminus \{\ell+1\}$.

The above procedure suggests how to find $(x^{(\ell+1)},y^{(\ell+1)})$ from $(x^{(\ell)},y^{(\ell)})$. The Dom2IP algorithm initializes with $(x^{(0)},y^{(0)})=(x,y)$ and  iteratively calls this procedure in order to obtain $(x^{(t)},y^{(t)})$. 
\iffalse{
\begin{algorithm}[H]
	\KwIn{$(x,y)\in \dom(S)$}
	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq x$}
	$x^{(0)}\leftarrow x$\\
	\For{$\ell = 0$ \textbf{to} $t-1$}{
		$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
		$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
		$y^{(\ell+1)}\leftarrow$ optimal solution for $w$ variables in $ \DOMtoS(x^{(\ell)})$\\
		\eIf{$\eta = 0$}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 0$\
		}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 1$
		}
	}
	\label{domtoIPalg}
	\caption{The Dom2IP algorithm}
\end{algorithm}
}\fi
We prove that indeed $(x^{(t)},y^{(t)})\in S$.

	First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of DomtoIP the $\DOMtoS(x^{\ell})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
	\begin{align*}
	\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
	\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
	\end{align*}
	Notice that if $\LP^{(\ell)}$ is a non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible. We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$. First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$. By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$. Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$. So if $x^{(0)}_j=0$, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$. Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$. Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.

@@

	We consider two cases. In the first case, we have $z^*_{\ell+1}=0$. In this case we have $x^{(\ell+1)}_{\ell+1}=0$. Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$. Also, $(z^*,w^*)\in P$. By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ . We have
	\begin{equation}
	\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
	\end{equation}
	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$. Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$. Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$. We claim that $(z,w)\in \IP^{(\ell+1)}$. If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$. Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$. Consider iteration $j$ of the Dom2IP algorithm. Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$. We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero. However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0. This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.

@@

	Now consider $(x^{(t)},y^{(t)})$. Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$. If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$. If $x^{(t)} =1$, it must be the case that $z_t > 0$. By the argument above there is a point $(z',w')\in \IP^{(t-1)}$. We show that $x^{(t)} = z'$. Observe that for $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$. We just need to show that $z'_j = 1$. Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution. This concludes the proof of Lemma \ref{domlemma}.

@@

\iffalse{
\begin{algorithm}[H]\label{FDTFull}
	\KwIn{$P= \{(x,y)\in \bbbr^{n\times p}: Ax+Gy\geq b\}$ and $S=\{(x,y)\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \bbbr^n_+ }\frac{\min_{(x,y)\in }cx}{\min_{(x,y)\in P}cx}$ is finite, $(x^*,y^*)\in P$}
	\KwOut{$(z^i,w^i)\in S$ and $\lambda_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\lambda_i = 1$, and $\sum_{i=1}^{k}\lambda_iz^i\leq g^tx^*$ }
	$L^0\leftarrow [(x^*,y^*),1]$\\
	\For{$i=1$ \textbf{to} $t$}{
		$L'\leftarrow \emptyset$\\
		\For{$[(x,y),\lambda] \in L^i$}{
			Apply Lemma \ref{round-up} to obtain $[(\hat{x}^0,\hat{y}^0),\gamma_0]$ and $[(\hat{x}^1,\hat{y}^1),\gamma_1]$\\
			$L' \leftarrow L' \cup \{[(\hat{x}^0,\hat{y}^0),\gamma_0]\} \cup \{[(\hat{x}^1,\hat{y}^1),\gamma_1]\}$\\			
		}
		Apply Lemma \ref{prune} to $L'$ to obtain $L^{i+1}$. 
	}
	\For{$[(x,y),\lambda] \in L^t$}{
		Apply Algorithm \ref{domtoIP} to $(x,y)$ to obtain $(z,w)\in S$\\
		$F \leftarrow F \cup \{[(z,w),\lambda]\}$
	}
	\textbf{return} $F$
	\caption{Fractional Decomposition Tree Algorithm}
\end{algorithm}}\fi

\section{FDT on binary MIPs}
\label{binaryfdt}

Assume we are given a point $(x^*,y^*)\in P$. For instance, $(x^*,y^*)$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.  In this section, we prove Theorem \ref{binaryFDT} by describing the Fractional Decomposition Tree (FDT) algorithm.
\iffalse{We also remark that if $g_I=1$, then the algorithm will give an exact decomposition of any feasible solution. }\fi

The FDT algorithm grows a tree similar to the classic branch-and-bound search tree for integer programs. Each node represents a partially integral vector $(\bar{x},\bar{y})$ in $\dom(P)$ together with a multiplier $\bar{\lambda}$. The solutions contained in the nodes of the tree become progressively more integral at each level. In each level of the tree, the algorithm maintain a conic combination of points with the properties mentioned above. Leaves of the FDT tree contain solutions with integer values for all the $x$ variables that dominate a point in $P$. We will later see how we can turn these into points in $S$.

@@

	Let $(x^0,y^0),(x^1,y^1)$, and $\gamma_0,\gamma_1$ be an optimal solution solution to the LP above. Let $(\hat{x}^0,\hat{y}^0) = (\frac{x^0}{\gamma_0},\frac{y^0}{\gamma_0})$, $(\hat{x}^1,\hat{y}^1) = (\frac{x^1}{\gamma_1},\frac{y^1}{\gamma_1})$. Observe that  (ii), (iii), (iv) are satisfied with this choice. In order to show that (i) is also satisfied we prove the following claim.

@@

	Suppose by induction that we have constructed sets $L_0,\ldots,L_i$. Let the solutions in $L_i$ be $(x^j,y^j)$ for $j=1,\ldots,k$ and $\lambda_j$ be their multipliers, respectively. For each $j= 1,\ldots,k$ by Lemma \ref{round-up} (setting $(x',y')= (x^j,y^j)$ and $\ell = i+1$) we can find $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and $\lambda^0_j$, $\lambda^1_j$ with the properties (i) to (v) in Lemma \ref{round-up}. Define $L'$ to be the set of nodes with solutions $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and multipliers  $\lambda_j\lambda^0_j$, $\lambda_j\lambda^1_j$, respectively, for $j=1,\ldots,k$. It is easy to check that \iffalse{
	Notice that for each $j= 1,\ldots,k$ by property (v) in Lemma \ref{round-up} we have $x_h^{j0}, x_h^{j1}\in \{0,1\}$ for $h = 0,\ldots,i+1$. We also have
	\begin{align*}
		\sum_{[(x,y),\lambda]\in L'} \lambda & =  \sum_{j=1}^{k} \lambda_j\lambda^0_j+\lambda_j\lambda^1_j&\\
		& \geq \sum_{j=1}^{k} \frac{\lambda_j}{ g} & (\text{By property (i) in Lemma \ref{round-up}})\\
		& \geq \frac{1}{g} \sum_{[(x,y),\lambda]\in L_i}\lambda&\\
		& \geq \frac{1}{g^{i+1}}.&(\text{By induction hypothesis})	 
	\end{align*} 
	Also 
	\begin{align*}
		\sum_{[(x,y),\lambda]\in L'}\lambda x & =  \sum_{j=1}^{k} \lambda_j\big(\lambda^0_jx^{j0}+\lambda^1_jx^{j1}\big)&\\ 
		& \leq \sum_{j=1}^{k} \lambda_j x^j  & (\text{By property (iv) in Lemma \ref{round-up}})\\
		& \leq \sum_{[(x,y),\lambda]\in L_i}\lambda x&\\
		& \leq x^*.&(\text{By induction hypothesis})	 
	\end{align*} \fi set $L'$ is a suitable candidate for $L_{i+1}$, i.e. set $L'$ satisfies (a), (b) and (c). However we can only ensure that $|L'|\leq 2k\leq 2t$, and might have $|L'|>t$. We call the following linear program $\prun(L')$. Let $L' = \{[(x^1,y^1),\gamma_1],\ldots,[(x^{2k},y^{2k}),\gamma_{2k}]\}$. The variables of $\prun(L')$ is a scalar variable $\theta_j$ for each node $j$ in $L'$.  
	\begin{align}
		\prun(L')\quad\quad& \max\quad \;\sum_{j=1}^{2k} \theta_j\\
		&\;\text{s.t.} \quad \;\;\sum_{j=1}^{2k} \theta_j x^j_i\leq x^*_i &\mbox{ for $i=1,\ldots,t$} \label{packs}\\
		&\;{\color{white}{\text{s.t.}} }\quad  \;\quad\quad\theta \geq 0\label{nonneg}
	\end{align}

	Notice that $\theta = \gamma$ is in fact a feasible solution to $\prun(L')$. Let $\theta^*$ be the optimal vertex point solution to this LP. Since the problem is in $\bbbr^{2k}$,  $\theta^*$ has to satisfy $2k$ linearly independent constraints at equality. However, there are only $t$ constraints of type (\ref{packs}). Therefore, there are at most $t$ coordinates of $\theta^*_j$ that are non-zero. We claim that $L_{i+1}$ which consists of $(x^j,y^j)$ for $j=1,\ldots,2k$ and their corresponding multipliers $\theta^*_j$ satisfy the properties in the statement of the lemma. Notice that, we can discard the nodes in $L_{i+1}$ that have $\theta^*_j=0$, so $|L_{i+1}| \leq t$. Also, since $\theta^*$ is optimal and $\gamma$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{k} \theta^*_j \geq \sum_{j=1}^{2k}\gamma_j \geq \frac{1}{g^{i+1}}$. 
\end{proof}
\paragraph{From leaves of FDT to feasible solutions}
For the leaves of the FDT tree,  $L_t$, we have that every solution $(x,y)$ in $L_t$ has $x\in\{0,1\}^n$ and $(x,y)\in \dom(P)$. By applying Lemma \ref{domlemma} we can obtain a point $(x',y')\in S$ such that $x'\leq x$. This conclude the description of the FDT algorithm and proves Theorem \ref{binaryFDT}.

>>>>

\section{Finding a feasible solution}\label{domTOIP}
Consider a formulation instance $I=(A,G,b)$. Define sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively. Assume $S(I),P(I)\in [0,1]^n\times \mathbb{R}^p$. For simplicity in the notation we denote $P(I),S(I),$ and $g(I)$ with $P$, $S$, and $g$ for this section and the next section. Also, for both sections we assume $t=|\spp(x)|$. Without loss of generality we can assume $x_i = 0$ for $i=t+1,\ldots,n$.

In this section we prove Theorem \ref{domtoIP}. In fact, we prove a stronger result. 
\begin{lemma}\label{domlemma}
	Given $(x,y)\in \dom(P)$, there is an algorithm (the DomToIP algorithm) that finds $(\bar{x},\bar{y})\in S$ in polynomial time, such that $\bar{x}\leq x$.\end{lemma}

We prove Lemma \ref{domlemma} by introducing an algorithm that ``fixes" the variables iteratively, starting from $x_1$ and ending at $x_t$. Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,t$. Now consider the following linear program. The variables of this linear program are the $z\in \mathbb{R}^n$ variables and $w\in \mathbb{R}^p$.
\begin{align}
	\DOMtoS(x^{(\ell)})\quad\quad& \min\quad \;z_{\ell+1}\\
	&\;\text{s.t.} \quad \;\;Az+ Gw\geq b \\
	&\;{\color{white}{\text{s.t.}} }\quad \;\; \; z_j = x^{(\ell)}_j \quad \; j =1,\ldots, \ell\\
	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z_j \leq x^{(\ell)}_j \quad \; j = \ell+1,\ldots,n\\
	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z\;\geq 0
\end{align}

If the optimal value to $\DOMtoS(x^{(\ell)})$ is 0, then let $x^{(\ell+1)}_{\ell+1} = 0$. Otherwise if the optimal value is strictly positive let $x^{(\ell+1)}_{\ell+1} = 1$. Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in \{1,\ldots,n\}\setminus \{\ell+1\}$ (See Algorithm \ref{domtoIPalg}).

The above procedure suggests how to find $(x^{(\ell+1)},y^{(\ell+1)})$ from $(x^{(\ell)},y^{(\ell)})$. The Dom2IP algorithm initializes with $(x^{(0)},y^{(0)})=(x,y)$ and  iteratively calls this procedure in order to obtain $(x^{(t)},y^{(t)})$.

\vspace*{10pt}
\begin{algorithm}[H]
	\KwIn{$(x,y)\in \dom(S)$}
	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq x$}
	$x^{(0)}\leftarrow x$\\
	\For{$\ell = 0$ \textbf{to} $t-1$}{
		$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
		$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
		$y^{(\ell+1)}\leftarrow$ optimal solution for $w$ variables in $ \DOMtoS(x^{(\ell)})$\\
		\eIf{$\eta = 0$}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 0$\
		}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 1$
		}
	}
	\caption{The DomToIP algorithm}
	\label{domtoIPalg}
\end{algorithm}
\vspace*{10pt}
We prove that indeed $(x^{(t)},y^{(t)})\in S$. First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of DomtoIP the $\DOMtoS(x^{\ell})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
	\begin{align*}
	\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
	\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
	\end{align*}
	Notice that if $\LP^{(\ell)}$ is a non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible. We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$. First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$. By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$. Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$. So if $x^{(0)}_j=0$, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$. Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$. Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.

@@

	We consider two cases. In the first case, we have $z^*_{\ell+1}=0$. In this case we have $x^{(\ell+1)}_{\ell+1}=0$. Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$. Also, $(z^*,w^*)\in P$. By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ . We have $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}$
	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$. Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$. Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$. We claim that $(z,w)\in \IP^{(\ell+1)}$. If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$. Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$. Consider iteration $j$ of the Dom2IP algorithm. Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$. We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero. However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0. This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.

@@

	Now consider $(x^{(t)},y^{(t)})$. Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$. If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$. If $x^{(t)} =1$, it must be the case that $z_t > 0$. By the argument above there is a point $(z',w')\in \IP^{(t-1)}$. We show that $x^{(t)} = z'$. For $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$. We just need to show that $z'_j = 1$. Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution. This concludes the proof of Lemma \ref{domlemma}.

@@

\section{FDT on binary MILPs}
\label{binaryfdt}

Assume we are given a point $(x^*,y^*)\in P$. For instance, $(x^*,y^*)$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.  In this section, we prove Theorem \ref{binaryFDT} by describing the Fractional Decomposition Tree (FDT) algorithm. We also remark that if $g_I=1$, then the algorithm will give an exact decomposition of any feasible solution.

The FDT algorithm grows a tree similar to the classic branch-and-bound search tree for integer programs. Each node represents a partially integral vector $(\bar{x},\bar{y})$ in $\dom(P)$ together with a multiplier $\bar{\lambda}$. The solutions contained in the nodes of the tree become progressively more integral at each level. In each level of the tree, the algorithm maintain a conic combination of points with the properties mentioned above. Leaves of the FDT tree contain solutions with integer values for all the $x$ variables that dominate a point in $P$. In Lemma  \ref{domlemma} we saw how to turn these into points in $S$.

@@

	Let $(x^0,y^0),(x^1,y^1)$, and $\gamma_0,\gamma_1$ be an optimal solution solution to the LP above. Let $(\hat{x}^0,\hat{y}^0) = (\frac{x^0}{\gamma_0},\frac{y^0}{\gamma_0})$, $(\hat{x}^1,\hat{y}^1) = (\frac{x^1}{\gamma_1},\frac{y^1}{\gamma_1})$. This choice satisfies  (ii), (iii), (iv). To show that (i) is also satisfied we prove the following claim.

@@

	Suppose by induction that we have constructed sets $L_0,\ldots,L_i$. Let the solutions in $L_i$ be $(x^j,y^j)$ for $j=1,\ldots,k$ and $\lambda_j$ be their multipliers, respectively. For each $j= 1,\ldots,k$ by Lemma \ref{round-up} (setting $(x',y')= (x^j,y^j)$ and $\ell = i+1$) we can find $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and $\lambda^0_j$, $\lambda^1_j$ with the properties (i) to (v) in Lemma \ref{round-up}. Define $L'$ to be the set of nodes with solutions $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and multipliers  $\lambda_j\lambda^0_j$, $\lambda_j\lambda^1_j$, respectively, for $j=1,\ldots,k$. It is easy to check that \iffalse{
	Notice that for each $j= 1,\ldots,k$ by property (v) in Lemma \ref{round-up} we have $x_h^{j0}, x_h^{j1}\in \{0,1\}$ for $h = 0,\ldots,i+1$. We also have
	\begin{align*}
		\sum_{[(x,y),\lambda]\in L'} \lambda & =  \sum_{j=1}^{k} \lambda_j\lambda^0_j+\lambda_j\lambda^1_j&\\
		& \geq \sum_{j=1}^{k} \frac{\lambda_j}{ g} & (\text{By property (i) in Lemma \ref{round-up}})\\
		& \geq \frac{1}{g} \sum_{[(x,y),\lambda]\in L_i}\lambda&\\
		& \geq \frac{1}{g^{i+1}}.&(\text{By induction hypothesis})	 
	\end{align*} 
	Also 
	\begin{align*}
		\sum_{[(x,y),\lambda]\in L'}\lambda x & =  \sum_{j=1}^{k} \lambda_j\big(\lambda^0_jx^{j0}+\lambda^1_jx^{j1}\big)&\\ 
		& \leq \sum_{j=1}^{k} \lambda_j x^j  & (\text{By property (iv) in Lemma \ref{round-up}})\\
		& \leq \sum_{[(x,y),\lambda]\in L_i}\lambda x&\\
		& \leq x^*.&(\text{By induction hypothesis})	 
	\end{align*} \fi set $L'$ is a suitable candidate for $L_{i+1}$, i.e. set $L'$ satisfies (a), (b) and (c). However we can only ensure that $|L'|\leq 2k\leq 2t$, and might have $|L'|>t$. We call the following linear program $\prun(L')$. Let $L' = \{[(x^1,y^1),\gamma_1],\ldots,[(x^{|L'|},y^{|L'|}),\gamma_{|L'|}]\}$. The variables of $\prun(L')$ are scalar variables $\theta_j$ for each node $j$ in $L'$.  
	\begin{equation}
		\prun(L')=\{\max \sum_{j=1}^{|L'|} \theta_j\;:\; \sum_{j=1}^{|L'|} \theta_j x^j_i\leq x^*_i \mbox{ for $i=1,\ldots,t$},\; \theta\geq 0 \}
	\end{equation}

	Notice that $\theta = \gamma$ is in fact a feasible solution to $\prun(L')$. Let $\theta^*$ be the optimal vertex point solution to this LP. Since the problem is in $\mathbb{R}^{|L'|}$,  $\theta^*$ has to satisfy $|L'|$ linearly independent constraints at equality. However, there are only $t$ constraints of type $ \sum_{j=1}^{|L'|} \theta_j x^j_i\leq x^*_i$. Therefore, there are at most $t$ coordinates of $\theta^*_j$ that are non-zero. Set $L_{i+1}$ which consists of $(x^j,y^j)$ for $j=1,\ldots,|L'|$ and their corresponding multipliers $\theta^*_j$ satisfy the properties in the statement of the lemma. Notice that, we can discard the nodes in $L_{i+1}$ that have $\theta^*_j=0$, so $|L_{i+1}| \leq t$. Also, since $\theta^*$ is optimal and $\gamma$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{|L'|} \theta^*_j \geq \sum_{j=1}^{|L'|}\gamma_j \geq \frac{1}{g^{i+1}}$. 
\end{proof}

\paragraph{From leaves of FDT to feasible solutions}
For the leaves of the FDT tree,  $L_t$, we have that every solution $(x,y)$ in $L_t$ has $x\in\{0,1\}^n$ and $(x,y)\in \dom(P)$. By applying Lemma \ref{domlemma} we can obtain a point $(x',y')\in S$ such that $x'\leq x$. This conclude the description of the FDT algorithm and proves Theorem \ref{binaryFDT}. See Algorithm \ref{FDTFull} for a summary of the FDT algorithm.

	\vspace*{10pt}

	\begin{algorithm}[H]\label{FDTFull}
		\KwIn{$P= \{(x,y)\in \mathbb{R}^{n\times p}: Ax+Gy\geq b\}$ and $S=\{(x,y)\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \mathbb{R}^n_+ }\frac{\min_{(x,y)\in }cx}{\min_{(x,y)\in P}cx}$ is finite, $(x^*,y^*)\in P$}
		\KwOut{$(z^i,w^i)\in S$ and $\lambda_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\lambda_i = 1$, and $\sum_{i=1}^{k}\lambda_iz^i\leq g^tx^*$ }
		$L^0\leftarrow [(x^*,y^*),1]$\\
		\For{$i=1$ \textbf{to} $t$}{
			$L'\leftarrow \emptyset$\\
			\For{$[(x,y),\lambda] \in L^i$}{
				Apply Lemma \ref{round-up} to obtain $[(\hat{x}^0,\hat{y}^0),\gamma_0]$ and $[(\hat{x}^1,\hat{y}^1),\gamma_1]$\\
				$L' \leftarrow L' \cup \{[(\hat{x}^0,\hat{y}^0),\gamma_0]\} \cup \{[(\hat{x}^1,\hat{y}^1),\gamma_1]\}$\\			
			}
			Apply Lemma \ref{prune} to $L'$ to obtain $L^{i+1}$. 
		}
		\For{$[(x,y),\lambda] \in L^t$}{
			Apply Algorithm \ref{domtoIPalg} to $(x,y)$ to obtain $(z,w)\in S$\\
			$F \leftarrow F \cup \{[(z,w),\lambda]\}$
		}
		\textbf{return} $F$
		\caption{Fractional Decomposition Tree Algorithm}
	\end{algorithm}
